### 2021-02-24 rad-icfp-2021/intro.tex
outline paper in intro

\begin{example}[First-order term]
On simple first-order terms, the output code looks like SSA code \cite{}.
Let's consider $\letin{w_1}{\var_1 * \var_2}{\letin{w_2}{w_1 * \var_1}{w_2}}$ in the context $\Gamma:=\{x1,x2,x3:\RR\}$.\\
After our inefficient reverse-mode transformation we obtain
\begin{align*}
    &\letin{w_1,w_1'}{\tPair{\var_1 * \var_2}{\inllambda \var[2]_1...\var[2]_4.Id(\var[2]_1+\var_2*\var[2]_4,\var[2]_2+\var_1*\var[2]_4,\var[2]_3)} }{
    \\
    &\letin{w_2,w_2'}{\tPair{w_1 * \var_1}{\inllambda \var[2]_1...\var[2]_5.w_1'(\var[2]_1+w_1 * \var[2]_5,\var[2]_2,\var[2]_3,\var[2]_4+ \var_1 * \var[2]_5)}}{\\ 
    & w_2'(0,0,0,0,1)}}
\end{align*}
where $Id$ is the identity function $\RR^3\to\RR^3$, $\inllambda$ is just a normal $\lambda$ tagged for inlining.
The part $(0,0,0,0,1)$ comes as an equivalent to initialing the tangent variables in the imperative reverse-mode algorithm.

@@

Our work looks like a compilation scheme, which is the following:

\input{figures/compilation_scheme}

>>>>

\begin{example}[First-order term]
On simple first-order terms, the output code looks like SSA code \cite{}.
\MH{need to rewrite following my notation.}
Let's consider $\letin{w_1}{\var_1 * \var_2}{\letin{w_2}{w_1 * \var_1}{w_2}}$ in the context $\Gamma:=\{x1,x2,x3:\RR\}$.\\
After our inefficient reverse-mode transformation we obtain
\begin{align*}
    &\letin{w_1,w_1'}{\tPair{\var_1 * \var_2}{\inllambda \var[2]_1...\var[2]_4.Id(\var[2]_1+\var_2*\var[2]_4,\var[2]_2+\var_1*\var[2]_4,\var[2]_3)} }{
    \\
    &\letin{w_2,w_2'}{\tPair{w_1 * \var_1}{\inllambda \var[2]_1...\var[2]_5.w_1'(\var[2]_1+w_1 * \var[2]_5,\var[2]_2,\var[2]_3,\var[2]_4+ \var_1 * \var[2]_5)}}{\\ 
    & w_2'(0,0,0,0,1)}}
\end{align*}
where $Id$ is the identity function $\RR^3\to\RR^3$, $\inllambda$ is just a normal $\lambda$ tagged for inlining.
The part $(0,0,0,0,1)$ comes as an equivalent to initialing the tangent variables in the imperative reverse-mode algorithm.

@@

Our work looks like the following compilation scheme
\input{figures/compilation_scheme}

In Section~\ref{sec:background} we recall reduminents of automatic differentiation, and in particular the idea of reverse-mode and the cheap gradient principle.
Next, in Section~\ref{sec:simplediff} we introduce the source language we want to differentiate. We also introduce our new intermediate representation UNF, and a simple reverse-mode macro on this representation.
In Section~\ref{sec:efficientrad} we translate back from UNF to a purely functional target language and show several general optimisations to make our reverse-mode transformation efficient.
In the next Section~\ref{sec:complexity} we show that the previous optimisations are sufficient to ensure our transformation has the right complexity.
Section~\ref{sec:correctness} shows that our construction is correct and we give standard semantics to our source and target languages. 
In Section~\ref{sec:generalisation} we show how to generalise the previous sections for a richer source language. 
Finally, related work and some limitations to our approach are presentend in Section~\ref{sec:conclusion}.
